Visual Search and Pre-crastination

### 2023-08-31 analysis/1_processing.Rmd
starting to process personality data

```{r}
dat %>% 
  group_by(person, site) %>%
  summarise(
    sensible = sum(choice == "sensible"),
    pre_crastinate = sum(choice != "sensible")) %>%
  mutate(
    classification = case_when(
      sensible > 4 ~ "no",
      sensible < 3 ~ "yes",
      TRUE ~ "intermediate"),
    classification = as_factor(classification),
    classification = fct_relevel(classification, 
                                 "no", "intermediate", "yes")) %>%
  select(person, site,
         n_pc = pre_crastinate, 
         pre_crastinate = "classification") %>%
  full_join(dat_shls) %>% na.omit -> dat

write_csv(dat, "scratch/pre_crastinate_clean.csv")
```

We have `r length(unique(dat$person))` people with data for both visual search and pre-crastination.

@@

Read in personality data and compute overall scores

>>>>

```{r}
dat %>% 
  group_by(person, site) %>%
  summarise(
    sensible = sum(choice == "sensible"),
    pre_crastinate = sum(choice != "sensible")) %>%
  mutate(
    classification = case_when(
      sensible > 4 ~ "no",
      sensible < 3 ~ "yes",
      TRUE ~ "intermediate"),
    classification = as_factor(classification),
    classification = fct_relevel(classification, 
                                 "no", "intermediate", "yes")) %>%
  select(person, site,
         n_pc = pre_crastinate, 
         pre_crastinate = "classification") %>%
  full_join(dat_shls) -> dat

@@

Read in personality data and compute overall scores.

```{r}
dat_p <- read_csv("../data/personsonality_q.csv")

# creating list of questions
procras_qs <- names(dat_p)[str_detect(names(dat_p), "ProScale")]
bfi_qs <-     names(dat_p)[str_detect(names(dat_p), "BFI")]
bis_qs <-     names(dat_p)[str_detect(names(dat_p), "BIS")]

# variables to reverse code
rev_code <- c("BFI2_03", "BFI2_04", "BFI2_05", "BFI2_08", "BFI2_09", "BFI2_11", 
              "BFI2_12", "BFI2_16", "BFI2_17", "BFI2_22", "BFI2_23", "BFI2_24", 
              "BFI2_25", "BFI2_26", "BFI2_28", "BFI2_29", "BFI2_30", "BFI2_31", 
              "BFI2_36", "BFI2_37", "BFI2_42", "BFI2_44", "BFI2_45", "BFI2_47", 
              "BFI2_48", "BFI2_49", "BFI2_50", "BFI2_51", "BFI2_55", "BFI2_58", 
              "ProScale_03", "ProScale_04", "ProScale_06", "ProScale_08", "ProScale_11", 
              "ProScale_13", "ProScale_14", "ProScale_15", "ProScale_18", "ProScale_20", 
              "BIS11_01", "BIS11_07", "BIS11_08", "BIS11_09", "BIS11_10", "BIS11_12", 
              "BIS11_13", "BIS11_15", "BIS11_20", "BIS11_29", "BIS11_30")

for (var in rev_code) {
  dat_p <- mutate(dat_p, "{var}r" := max(!!as.name(var), na.rm = T) - !!as.name(var) + 1) 
}
rm(var)

# create Big 5 measures
# 
# Extraversion: 1, 6, 11R, 16R, 21, 26R, 31R, 36R, 41, 46, 51R, 56
# Agreeableness: 2, 7, 12R, 17R, 22R, 27, 32, 37R, 42R, 47R, 52, 57
# Conscientiousness: 3R, 8R, 13, 18, 23R, 28R, 33, 38, 43, 48R, 53, 58R
# Negative Emotionality: 4R, 9R, 14, 19, 24R, 29R, 34, 39, 44R, 49R, 54, 59
# Open-Mindedness: 5R, 10, 15, 20, 25R, 30R, 35, 40, 45R, 50R, 55R, 60

dat_p %>% select(person, starts_with("BFI2_")) %>%
  pivot_longer(-person, names_to = "item", values_to = "resp") %>%
  separate(item, into = c("BFI", "item")) %>%
  select(-BFI) %>%
  pivot_wider(person, names_from = "item", values_from = "resp") %>%
  mutate(extraversion = 
           rowMeans(select(., '01', '06', '11r', '21', '26r', '31r', '36r', '41', '46', '51r', '56')),
         agreeableness = 
           rowMeans(select(., '02', '07', '12r', '17r', '22r', '27', '32', '37r', '42r', '47r', '52', '57')),
         conscientiousness = 
           rowMeans(select(., '03r', '08r', '13', '18', '23r', '28r', '33', '38', '43', '48r', '53', '58r')),
         negative_emo = 
           rowMeans(select(., '04r', '09r', '14', '19', '24r', '29r', '34', '39', '44r', '49r', '54', '59')),
         open_mindedness = 
           rowMeans(select(., '05r', '10', '15', '20', '25r', '30r', '35', '40', '45r', '50r', '55r', '60'))) %>%
  select(person = "person", extraversion, agreeableness, conscientiousness, negative_emo, open_mindedness) -> d_BFI

# create procrastination variable
procras_qs_rev <- paste0(procras_qs[which(procras_qs %in% rev_code)], "r")
procras_qs_fwd <- procras_qs[which(!(procras_qs %in% rev_code))]
procras_qs <- c(procras_qs_fwd, procras_qs_rev)
rm(procras_qs_fwd, procras_qs_rev)

dat_p %>% pivot_longer(procras_qs, names_to = "ProscaleID", values_to = "score") %>%
  group_by(person) %>%
  summarise(procrastination =  mean(score)) %>%
  rename(person = "person") %>%
  full_join(d_BFI, by = "person") -> dat_p2

rm(d_BFI)

dat_p %>% select(person, starts_with("BIS11_")) %>%
  pivot_longer(-person, names_to = "item", values_to = "resp") %>%
  separate(item, into = c("BIS", "item")) %>%
  select(-BIS) %>%
  pivot_wider(id_cols = person, names_from = "item", values_from = "resp") %>%
  mutate(BIStotal = 
           rowMeans(select(., '01r', '02', '03', '04', '05', '06', '07r', '08r', '09r', '10r', '11', '12r', '13r', '14', '15r', '16', '17', '18', '19', '20r', '21', '22', '23', '24', '25', '26', '27', '28', '29r', '30r')),
         attentional_imp = 
           rowMeans(select(., '05', '09r', '11', '20r', '28', '06', '24', '26')),
         motor_imp = 
           rowMeans(select(., '02', '03', '04', '17', '19', '22', '25', '16', '21', '23', '30r')),
         nonplan_imp = 
           rowMeans(select(., '01r', '07r', '08r', '12r', '13r', '14', '10r', '15r', '18', '27', '29r'))) %>%
  select(person = "person", BIStotal, attentional_imp, motor_imp, nonplan_imp)  %>%
  full_join(dat_p2, by = "person") -> dat_p2

d_out2 <- full_join(d_out, d %>% rename(person = "person")) %>%
  select(-c(LocationLatitude, LocationLongitude, 
            ResponseId, Finished, Duration_in_Seconds, `Duration (in seconds)`,
            StartTime, EndTime))
